|

### 2020-01-06 nontex/install/windows/fn_installations.Rmd
several additional apms

```
{
  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
  "window.zoomLevel": 0,
  "latex-workshop.view.pdf.viewer": "external",
  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
  "latex-workshop.view.pdf.external.synctex.args": [
		"-forward-search",
		"%TEX%",
		"%LINE%",
		"-reuse-instance",
		"-inverse-search",
		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
		"%PDF%",
	],
	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
}
```
## Atom Installation

@@

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
# apm install project-manager
apm install sublime-style-column-selection
apm install minimap

@@

@@

@@

>>>>

```
{
  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
  "window.zoomLevel": 0,
  "latex-workshop.view.pdf.viewer": "external",
  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
  "latex-workshop.view.pdf.external.synctex.args": [
		"-forward-search",
		"%TEX%",
		"%LINE%",
		"-reuse-instance",
		"-inverse-search",
		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
		"%PDF%",
	],
	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
}
```

## Atom Installation

@@

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
# apm install project-manager

@@

# Selection and Overview
apm install sublime-style-column-selection
apm install minimap
apm install highlight-selected

@@

# support
apm install date

@@

### Atom settings file

```
{
  "r.rterm.windows": "C:/Program Files/R/R-3.6.2/bin/x64/R.exe",
  "window.zoomLevel": 0,
  "latex-workshop.view.pdf.viewer": "external",
  "latex-workshop.view.pdf.external.synctex.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe",
  "latex-workshop.view.pdf.external.synctex.args": [
		"-forward-search",
		"%TEX%",
		"%LINE%",
		"-reuse-instance",
		"-inverse-search",
		"code \"C:\\Users\\fan\\AppData\\Local\\Programs\\Microsoft VS Code\\resources\\app\\out\\cli.js\" -r -g \"%f:%l\"",
		"%PDF%",
	],
	"latex-workshop.view.pdf.external.viewer.command": "C:/Program Files/SumatraPDF/SumatraPDF.exe"
}
```
